Renormalization

### 2014-05-21 papers/renormalization/paper.tex
more renormalization work Tested on bennet. Took 0:18.13.

\begin{figure}
  \centering
  \includegraphics[width=0.8\columnwidth]{figs/interactions}
  \caption{Interactions between neighboring subdivisions.}\label{fig:interactions}
\end{figure}

@@

We desire to simplify the summation over seven independent numbers
$N_1\cdots N_7$ (with the eighth constrained by $\sum_i N_i = N$) to a
summation over a single fluctuation amplitude.  As illustrated in
Fig.~\ref{fig:interactions}, these interactions can be seen as
a sum of interactions between neighboring subdivisions, combined with
a many-body correction due to ``corner'' interactions.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.8\columnwidth]{figs/interactions}
  \caption{Interactions between all subdivisions.}\label{fig:interactions}
\end{figure}

@@

We desire to simplify the summation over seven independent numbers
$N_1\cdots N_7$ (with the eighth constrained by $\sum_i N_i = N$) to a
summation over a single fluctuation amplitude.  As illustrated in
Fig.~\ref{fig:interactions}, these interactions can be seen as a sum
of interactions between neighboring subdivisions, combined with a
many-body corrections due to the free energy not being precisely
separable into additive pairwise contributions (due to for instance
``corner'' interactions).

\begin{figure}
  \centering
  \includegraphics[width=0.8\columnwidth]{figs/neighbors}
  \caption{Interactions between only neighboring subdivisions.}\label{fig:neighbors}
\end{figure}

If we make this assumption, that the free energy can be separated into
neighboring contributions, we can write
\begin{align}
  F_j(N_1\cdots N_8) &= \alpha \sum_{ij}^{\text{neighbors}} F_j^{\text{neighbor}}(N_i, N_j)
\end{align}
where $F_j^{\text{neighbor}}(N_i, N_j)$ is the free energy of the
system illustrated in Fig.~\ref{fig:neighbors}, which has a slab-like
density oscillation, and $\alpha$ \fixme{is a prefactor that I need to
  work out}.

I will note that we have a choice of lattice when defining our
periodic system.  At this point we can see that a simple cubic lattice
gives us a flat-slab neighbor system.  If we had chosen a close-packed
FCC lattice, then each subdivision would interact equally with all the
other subdivisions (and corners would involve four subdivisions rather
than all eight), but our slab geometry would have a bumpy interface
(e.g. if we chose a $\langle 111\rangle$ slab it would have an
equilateral triangular lattice of bumps).  I will continue thinking in
terms of a simple cubic interface, with the option to revise this to
switch lattices.

Once we have rewritten $F_j(N_1\cdots N_8)$ in terms of
$F_j^{\text{neighbor}}(N_i, N_j)$, we can further simplify our free energy
difference (and definitions of $\bar{U}$ and $\bar{F}$):
